Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-09 minimax.tex

\section{Empirical Evaluation} 
\label{sec:experiments}
%TODO
%\begin{enumerate}
%	\item Reach regret: $n/10$. For this, we need $m^x n$ questions. Wait for more runs (Correct formula)
%Graphs: order symbols in the legend. Reduce number of marks on the X axis.
%\end{enumerate}

@@

\subsection{Absolute evaluation of Pessimistic strategy}
\label{sec:lowRegret}
\begin{table}
	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
	\label{tab:lowRegret}
	\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
		\toprule
		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$0.4 m^{1.6} n$} \\
		\midrule
		5 & 10 & 1.0 & 60 &  55 \\
		5 & 15 & 1.5 & 80 &  83 \\
		5 & 20 & 2.0 & 110 &  110 \\
		10 & 20 & 2.0 & 340 &  341 \\
		10 & 30 & 3.0 & 527 &  512 \\
		15 & 30 & 3.0 & 812 &  991 \\
		\bottomrule
	\end{tabular}
\end{table}
\begin{table}
	\caption{Number of questions needed by the Pessimistic strategy to elicit the complete preference of one agent.}
	\label{tab:fullProfile}
	\begin{tabular}{S[table-figures-integer=2, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=2]}
		\toprule
		m & k \\
		\midrule
		5 & 6.6\\
		10 & 24.8\\
		15 & 48.4\\
		\bottomrule
	\end{tabular}
\end{table}

The previous section compares Pessimistic to other strategies. In this set of experiments, we wonder about the absolute quality of Pessimistic. For practical usability, it is important to know how many questions should be asked in order to reach a low regret level. Here, we consider a low level to be a tenth of the number of agents ($n/10$): such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
The results for various sizes are displayed in \cref{tab:lowRegret}. 
By relating the sizes to the column $k_{\MMR}$, we obtain the function $0.4m^{1.6}n$ as an approximation formula for the number of questions required to reach a low regret level. We see that this number grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives, for the sizes we considered. In other words, on average, assuming no questions get asked to the chair, each agent will have to answer $0.4m^{1.6}$ questions in order to to reach a low regret level, if this experimental formula reveals correct. For $m = 5$, that is about $6$ questions per agent; for $m = 10$, that is about $17$ questions per agent; and for $m = 15$, that is about $33$ questions per agent. These numbers have to be contrasted with those displayed in \cref{tab:fullProfile}. We constrained the Pessimistic strategy to ask questions to the agent only, and ran it on a single agent problem, with various values for $m$, to evaluate the number of questions required to elicit the full preference of an agent.

>>>>

\section{Empirical Evaluation} 
\label{sec:experiments}
%TODO
%\begin{enumerate}
%	\item Reach regret: $n/10$. For this, we need $m^x n$ questions. Wait for more runs (Correct formula)
%Graphs: order symbols in the legend. Reduce number of marks on the X axis.
%MMR and sd with systematically one decimal exactly
%\end{enumerate}

@@

\subsection{Absolute evaluation of Pessimistic strategy}
\label{sec:lowRegret}
\begin{table}
	\caption{Number of questions needed by Pessimistic strategy to reach an MMR of $\frac{n}{10}$ (represented by $k_{\MMR}$), by size.}
	\label{tab:lowRegret}
	\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
		\toprule
		{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} \\
		\midrule
		5 & 10 & 1.0 & 60 \\
		5 & 15 & 1.5 & 80 \\
		5 & 20 & 2.0 & 110 \\
		10 & 20 & 2.0 & 340 \\
		10 & 30 & 3.0 & 527 \\
		15 & 30 & 3.0 & 812 \\
		\bottomrule
	\end{tabular}
\end{table}
\begin{table}
	\caption{Number of questions needed by the Pessimistic strategy to elicit the complete preference of one agent.}
	\label{tab:fullProfile}
	\begin{tabular}{S[table-figures-integer=2, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=2]}
		\toprule
		m & k \\
		\midrule
		5 & 6.6\\
		10 & 24.8\\
		15 & 48.4\\
		\bottomrule
	\end{tabular}
\end{table}

The previous section compares Pessimistic to other strategies. In this set of experiments, we wonder about the absolute quality of Pessimistic. For practical usability, it is important to know how many questions should be asked in order to reach a low regret level. Here, we consider a low level to be a tenth of the number of agents ($n/10$): such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the agents rank $x$ last instead of first.
The results for various sizes are displayed in \cref{tab:lowRegret}. 
We see that the number of questions required to reach a low regret level grows approximately linearly with the number of agents and grows less fast than the square of the number of alternatives, for the sizes we considered. Averaging these data by category of value for $m$, and assuming no questions get asked to the chair, in order to to reach a low regret level, each agent will have to answer $5.6$ questions for $m = 5$, $17.2$ questions for $m = 10$ and $27.1$ questions for $m = 15$. These numbers have to be contrasted with those displayed in \cref{tab:fullProfile}, that estimate the number of questions required to elicit the full preference of an agent. To obtain the data for this table, we constrained the Pessimistic strategy to ask questions to the agents only, and ran it on a single agent problem, with various values for $m$.
